### 2016-07-18 version0.0/appendixa.tex
All chapter done

\chapter{SFR from H$\alpha$ Plus 24 \um: Procedure and Result}
\pagestyle{plain}
\label{app:halpha}
\myappendices
As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using \halpha emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of \halpha continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.

The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from \halpha using the scaling factor between fluxes in these two band passes determined by~\citet{Azimlu11}. They estimated continuum emission in each \halpha image, using photometric measurements in both \halpha and $R$-band images, and determined the scaling factor. These images were observed from a ground-based telescope over two years' time. Consequently, there is a non-negligible sky contribution in the background which must be estimated and removed from each image in both bands. Unfortunately, there is no nearby `blank-sky' image taken with the same instrument available from which to measure the sky contribution, which makes the removal of background emission even harder. The only remaining choice is to subtract the local background for each region. However, subtracting local backgrounds from each image will result in a non-smooth background in the final mosaic image.

\begin{figure}
\centering
\includegraphics[width=164mm]{../image_paper1/halpha.pdf}
\caption[Mosaic of H$\alpha$ emission images of M31]{Mosaic created using the Montage programme from six fields of \halpha emission images of M31 from \citet{Massey07}. The resulting image from Montage was continuum-subtracted and masked for all point sources. The centre of the galaxy was masked out due to saturation of data in the continuum $R$-band image.}
\label{fig:halpha}
\end{figure}

To create the final mosaic, first we removed the background from each region in both the \halpha\ and $R$-band images. The second step was to subtract the continuum from the \halpha images. Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image. At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin\ region in the centre of the galaxy. To account for the flux contribution of the \nii\ emission we used the flux ratio $\mathrm{\nii}/\mathrm{H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha\ map. We created the final mosaic image, Fig.\ref{fig:halpha}, using the Montage program~\citep{Berriman08}.

Creating the SFR map using \halpha plus 24~$\mu$m was described in Section~\ref{sec:sfr_halpha}. In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}. The fitting results using SFR(\halpha $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers. The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data. Thus we did not include the SFR(\halpha $+$ 24~$\mu$m) in our final analysis.

>>>>

\chapter{SFR from H$\alpha$ Plus 24 \um: Procedure and Result}
\pagestyle{plain}
\label{app:halpha}
\myappendices
As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha\ data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using \halpha\ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of \halpha\ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha\ filter from the \nii\ 6583~\AA\ line.

The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from \halpha\ using the scaling factor between fluxes in these two band passes determined by~\citet{Azimlu11}. They estimated continuum emission in each \halpha\ image, using photometric measurements in both \halpha\ and $R$-band images, and determined the scaling factor. These images were observed from a ground-based telescope over two years' time. Consequently, there is a non-negligible sky contribution in the background which must be estimated and removed from each image in both bands. Unfortunately, there is no nearby `blank-sky' image taken with the same instrument available from which to measure the sky contribution, which makes the removal of background emission even harder. The only remaining choice is to subtract the local background for each region. However, subtracting local backgrounds from each image will result in a non-smooth background in the final mosaic image.

\begin{figure}
\centering
\includegraphics[width=164mm]{../image_paper1/halpha.pdf}
\caption[Mosaic of H$\alpha$ emission images of M31]{Mosaic created using the Montage programme from six fields of \halpha\ emission images of M31 from \citet{Massey07}. The resulting image from Montage was continuum-subtracted and masked for all point sources. The centre of the galaxy was masked out due to saturation of data in the continuum $R$-band image.}
\label{fig:halpha}
\end{figure}

To create the final mosaic, first we removed the background from each region in both the \halpha\ and $R$-band images. The second step was to subtract the continuum from the \halpha\ images. Since both \halpha\ and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha\ image. At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin\ region in the centre of the galaxy. To account for the flux contribution of the \nii\ emission we used the flux ratio $\mathrm{\nii}/\mathrm{H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha\ map. We created the final mosaic image, Fig.\ref{fig:halpha}, using the Montage program~\citep{Berriman08}.

Creating the SFR map using \halpha\ plus 24~$\mu$m was described in Section~\ref{sec:sfr_halpha}. In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}. The fitting results using SFR(\halpha\ $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers. The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha\ data. Thus we did not include the SFR(\halpha\ $+$ 24~$\mu$m) in our final analysis.

### 2016-07-18 version0.0/appendixc.tex
All chapter done

\chapter[Self-Organizing Map for High-redshift galaxies]{Results of Training High-redshift Galaxies for one-dimensional self-organizing maps}
\pagestyle{plain}
\label{app: high_Z_1d_soms}
\newpage
\myappendices{
As mentioned in Sec.~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$. In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.

@@

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_20.png}
            %\caption{$1\times20$ weight map}
             %\label{fig: 1by20T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_20.png}
             %\caption{$1\times20$ hits map}
             %\label{fig: 1by20Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times20$~grid.}
         \label{fig: 1by20T}
    \end{figure}
    }

>>>>

\chapter[Self-Organizing Map for High-Redshift Galaxies]{Results of Training High-Redshift Galaxies for One-Dimensional Self-Organizing Maps}
\pagestyle{plain}
\label{app: high_Z_1d_soms}
\newpage
\myappendices

As mentioned in Section~\ref{sec: 1D_somz}, we changed the size of the SOM from $1\times2$ to $1\times22$. In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.

@@

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_20.png}
            %\caption{$1\times20$ weight map}
             %\label{fig: 1by20T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_20.png}
             %\caption{$1\times20$ hits map}
             %\label{fig: 1by20Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times20$~grid.}
         \label{fig: 1by20T}
    \end{figure}

### 2016-07-18 version0.0/paper1.tex
All chapter done

%P2: SFR, measuring, scaling, ...
In order to investigate star formation laws, the first step is to calculate the SFR. Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}. \citet{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.][]{Bruzual93}. Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands. \citet{Kennicutt09} and \citet{Hao11} introduced new SFR calibrations using a combination of \halpha or far-ultraviolet (FUV) and far-infrared (FIR) emission. In addition to using suitable calibrations for each region, considering the differences between the global and the local ($\sim 0.5-1$~\kpc) cases is important. In $\S$~\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.

@@

Several different observational datasets are used to compute properties of M31 for testing star formation laws.
One method for calculating the SFR uses FUV emission as a tracer of the star-forming regions: for this we
use the FUV image of M31 as observed by the Galaxy Evolution Explorer \citep[GALEX;][]{Martin05}. 
A second method to calculate the SFR involved using a combination of \halpha and 24~$\mu$m emission. \citet{Massey06, Massey07} mapped M31 in broad and narrow bands, including \halpha, as part of the Nearby Galaxies Survey using the KPNO 4-m telescope. A detailed description of how our \halpha map was made can be found in Appendix~\ref{app:halpha}.

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
Stellar population synthesis models make different assumptions about the IMF, often either \citet{Salpeter55},
$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or 
\citet{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$ for higher mass.
For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars. Different predictions of the number of stars between various IMFs are one of the main uncertainty sources in the calculation of the stellar mass \citep{Eskew12,Brewer12}. \citet{Eskew12} showed that the total mass of low-mass stars can change by a factor of 2.5 depending on the IMF.
\citet{Calzetti13} showed the impact of different IMF assumptions on SFR calibrations. Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators. Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.

@@

\subsubsection{\halpha plus 24 \um Star Formation Rate}
\label{sec:sfr_halpha}

The SFR can also be calculated using a combination of \halpha and \Spitzer  24 \um maps. \halpha emission of galaxies is dominated by light emitted from young and massive stars. Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}. Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}. However, \halpha emission is very sensitive to dust extinction. Therefore, the combination of the \halpha and 24\um of considered a better choice for calculating the SFR. We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
\begin{equation}
\label{equ: halphaplus24_g}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\mathrm obs} + 0.020L(24\mu m)],
\end{equation}
\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$. It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.

@@

\begin{table}
\begin{minipage}{100mm}
\caption{Comparison of the total star formation rate of M31}
\label{table:sfr}
\begin{tabular}{@{}lcc}
\hline\hline
Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
\hline
Current work&FUV and 24~$\mu$m&0.31 \\
Current work&\halpha and 24~$\mu$m&0.35 \\
Current work&TIR luminosity&0.4\\
\citet{Ford13}&FUV and 24~$\mu$m&0.25\\
\citet{Ford13}&TIR luminosity&0.48-0.52\\
\citet{Azimlu11}& \halpha and 24~$\mu$m&0.34\\
\citet{Azimlu11}&Extinction-corrected \halpha&0.44\\
\citet{Tabatabaei10}&Extinction-corrected \halpha&0.27--0.38\\
\citet{Barmby06}&Infrared 8\um luminosity& 0.4\\
\hline
\end{tabular}
\end{minipage}
\end{table}

@@

Fig.~\ref{fig:ks_all} shows the pixel-by-pixel fitting of the K-S law on the whole galaxy. The first row of plots are the surface density of the SFR(TIR), which is calculated using the TIR emission from Section~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$), only atomic gas (H\,{\textsc i}), and total gas from right to left, respectively. 
The only difference between the upper and the other rows is that in the lower rows the SFR indicator is FUV plus 24~$\mu$m (second row), and \halpha plus 24~$\mu$m emission (third row). Fig.~\ref{fig:ks,regs} shows the same data as Fig.~\ref{fig:ks_all}. However, in this figure we separated pixels from different regions in the galaxy by their colours. 
 There is a deviation in the middle panel plots of Fig.~\ref{fig:ks_all} which shows a set of points with with high star formation rate and low H\,{\textsc i} gas.
As can be clearly seen in middle panel of Fig.~\ref{fig:ks,regs}, this deviation is due to regions within 8~kpc of the centre of the galaxy (red points).
 \cite{Braun09} saw a similar feature in their studies of the K-S law in M31. 
The H\,{\textsc i} surface density profile of M31 \citep[see figure 16 in][]{Chemin09} shows several local minima from the centre of M31 out to 30~kpc distance which could be a result of the H\,{\textsc i} wrap. The H\,{\textsc i} surface density map shows a lower density in the central regions compared to the ring area; on the other hand, the SFR maps show high densities in the central regions. The combination of the relatively low gas and high SFR causes the deviation. However,~~\cite{Braun09} argued that the high 24~$\mu$m fluxes in the centre of the galaxy are due to other processes such as shock heating rather than a large amount of star formation.
Since the total gas mass is calculated by adding H\,{\textsc i} and H$_2$ gas mass, we can see this deviation in the right panel of Fig.~\ref{fig:ks_all} as well. However, since we have H$_2$ emission in those regions these deviations are less prominent than the ones in the middle panel.

>>>>

%P2: SFR, measuring, scaling, ...
In order to investigate star formation laws, the first step is to calculate the SFR. Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}. \citet{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.][]{Bruzual93}. Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands. \citet{Kennicutt09} and \citet{Hao11} introduced new SFR calibrations using a combination of \halpha\ or far-ultraviolet (FUV) and far-infrared (FIR) emission. In addition to using suitable calibrations for each region, considering the differences between the global and the local ($\sim 0.5-1$~\kpc) cases is important. In $\S$~\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.

@@

Several different observational datasets are used to compute properties of M31 for testing star formation laws.
One method for calculating the SFR uses FUV emission as a tracer of the star-forming regions: for this we
use the FUV image of M31 as observed by the Galaxy Evolution Explorer \citep[GALEX;][]{Martin05}. 
A second method to calculate the SFR involved using a combination of \halpha\ and 24~$\mu$m emission. \citet{Massey06, Massey07} mapped M31 in broad and narrow bands, including \halpha, as part of the Nearby Galaxies Survey using the KPNO 4-m telescope. A detailed description of how our \halpha\ map was made can be found in Appendix~\ref{app:halpha}.

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
Stellar population synthesis models make different assumptions about the IMF, often either \citet{Salpeter55},
$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or 
\citet{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$ for higher mass.
For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars. Different predictions of the number of stars between various IMFs are one of the main uncertainty sources in the calculation of the stellar mass \citep{Eskew12,Brewer12}. \citet{Eskew12} showed that the total mass of low-mass stars can change by a factor of 2.5 depending on the IMF.
\citet{Calzetti13} showed the impact of different IMF assumptions on SFR calibrations. Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators. Changes in the IMF mostly affect the calibration based on \halpha\ luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.

@@

\subsubsection{\halpha\ plus 24 \um Star Formation Rate}
\label{sec:sfr_halpha}

The SFR can also be calculated using a combination of \halpha\ and \Spitzer  24 \um maps. \halpha\ emission of galaxies is dominated by light emitted from young and massive stars. Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}. Therefore, \halpha\ alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}. However, \halpha\ emission is very sensitive to dust extinction. Therefore, the combination of the \halpha\ and 24\um of considered a better choice for calculating the SFR. We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
\begin{equation}
\label{equ: halphaplus24_g}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\mathrm obs} + 0.020L(24\mu m)],
\end{equation}
\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha\ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$. It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.

@@

\begin{table}
\begin{minipage}{100mm}
\caption{Comparison of the total star formation rate of M31}
\label{table:sfr}
\begin{tabular}{@{}lcc}
\hline\hline
Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
\hline
Current work&FUV and 24~$\mu$m&0.31 \\
Current work&\halpha\ and 24~$\mu$m&0.35 \\
Current work&TIR luminosity&0.4\\
\citet{Ford13}&FUV and 24~$\mu$m&0.25\\
\citet{Ford13}&TIR luminosity&0.48-0.52\\
\citet{Azimlu11}& \halpha\ and 24~$\mu$m&0.34\\
\citet{Azimlu11}&Extinction-corrected \halpha&0.44\\
\citet{Tabatabaei10}&Extinction-corrected \halpha&0.27--0.38\\
\citet{Barmby06}&Infrared 8\um luminosity& 0.4\\
\hline
\end{tabular}
\end{minipage}
\end{table}

@@

Fig.~\ref{fig:ks_all} shows the pixel-by-pixel fitting of the K-S law on the whole galaxy. The first row of plots are the surface density of the SFR(TIR), which is calculated using the TIR emission from Section~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$), only atomic gas (H\,{\textsc i}), and total gas from right to left, respectively. 
The only difference between the upper and the other rows is that in the lower rows the SFR indicator is FUV plus 24~$\mu$m (second row), and \halpha\ plus 24~$\mu$m emission (third row). Fig.~\ref{fig:ks,regs} shows the same data as Fig.~\ref{fig:ks_all}. However, in this figure we separated pixels from different regions in the galaxy by their colours. 
 There is a deviation in the middle panel plots of Fig.~\ref{fig:ks_all} which shows a set of points with with high star formation rate and low H\,{\textsc i} gas.
As can be clearly seen in middle panel of Fig.~\ref{fig:ks,regs}, this deviation is due to regions within 8~kpc of the centre of the galaxy (red points).
 \cite{Braun09} saw a similar feature in their studies of the K-S law in M31. 
The H\,{\textsc i} surface density profile of M31 \citep[see figure 16 in][]{Chemin09} shows several local minima from the centre of M31 out to 30~kpc distance which could be a result of the H\,{\textsc i} wrap. The H\,{\textsc i} surface density map shows a lower density in the central regions compared to the ring area; on the other hand, the SFR maps show high densities in the central regions. The combination of the relatively low gas and high SFR causes the deviation. However,~~\cite{Braun09} argued that the high 24~$\mu$m fluxes in the centre of the galaxy are due to other processes such as shock heating rather than a large amount of star formation.
Since the total gas mass is calculated by adding H\,{\textsc i} and H$_2$ gas mass, we can see this deviation in the right panel of Fig.~\ref{fig:ks_all} as well. However, since we have H$_2$ emission in those regions these deviations are less prominent than the ones in the middle panel.
